\begin{thebibliography}{99}\small
% =====================================================================

\bibitem{ref_sbert} N.\ Reimers and I.\ Gurevych, ``Sentence-BERT:
Sentence Embeddings using Siamese BERT-Networks,'' in
\emph{Proc.\ EMNLP}, 2019, pp.\ 3982--3992.

\bibitem{ref_e5} L.\ Wang, N.\ Yang, X.\ Huang, et al.,
``Text Embeddings by Weakly-Supervised Contrastive Pre-training,''
\emph{arXiv:2212.03533}, 2022.

\bibitem{ref_gtr} J.\ Ni et al., ``Large Dual Encoders Are Generalizable
Retrievers,'' in \emph{Proc.\ EMNLP}, 2022, pp.\ 9844--9855.

\bibitem{ref_bgem3} J.\ Chen, S.\ Xiao, P.\ Zhang, K.\ Luo, D.\ Lian,
and Z.\ Liu, ``BGE M3-Embedding: Multi-Lingual, Multi-Functionality,
Multi-Granularity Text Embeddings Through Self-Knowledge Distillation,''
\emph{arXiv:2402.03216}, 2024.

\bibitem{ref_dpr} V.\ Karpukhin et al., ``Dense Passage Retrieval for
Open-Domain Question Answering,'' in \emph{Proc.\ EMNLP}, 2020,
pp.\ 6769--6781.

\bibitem{ref_colbert} O.\ Khattab and M.\ Zaharia, ``ColBERT: Efficient
and Effective Passage Search via Contextualised Late Interaction over
BERT,'' in \emph{Proc.\ ACM SIGIR}, 2020, pp.\ 39--48.

\bibitem{ref_vec2text} J.\ X.\ Morris, V.\ Kuleshov, V.\ Shmatikov, and
A.\ M.\ Rush, ``Text Embeddings Reveal (Almost) As Much As Text,'' in
\emph{Proc.\ EMNLP}, 2023.

\bibitem{ref_geia} H.\ Li, M.\ Xu, and Y.\ Song, ``Sentence Embedding
Leaks More Information than You Expect: Generative Embedding Inversion
Attack to Recover the Whole Sentence,'' in \emph{Findings of ACL}, 2023,
pp.\ 14022--14040.

\bibitem{ref_teia} Y.-H.\ Huang, Y.\ Tsai, H.\ Hsiao, H.-Y.\ Lin, and
S.-D.\ Lin, ``Transferable Embedding Inversion Attack: Uncovering Privacy
Risks in Text Embeddings without Model Queries,'' in \emph{Proc.\ ACL
(Long)}, 2024, pp.\ 4193--4205.

\bibitem{ref_algen} Y.\ Chen, Q.\ Xu, and J.\ Bjerva, ``ALGEN:
Few-shot Inversion Attacks on Textual Embeddings via Cross-Model
Alignment and Generation,'' in \emph{Proc.\ ACL}, 2025.

\bibitem{ref_zsinvert} C.\ Zhang, J.\ X.\ Morris, and V.\ Shmatikov,
``Universal Zero-shot Embedding Inversion,'' \emph{arXiv:2504.00147},
2025.

\bibitem{ref_lago} W.\ Yu, Y.\ Chen, J.\ Bjerva, S.\ Kosta, and Q.\ Li,
``LAGO: Few-shot Crosslingual
Embedding Inversion Attacks via Language Similarity-Aware Graph
Optimization,'' \emph{arXiv:2505.16008}, 2025.

\bibitem{ref_eguard} T.\ Liu et al., ``EGuard: Defending LLM Embeddings
Against Inversion Attacks via Text Mutual Information Optimization,''
in \emph{Proc.\ AAAI}, 2026.

\bibitem{ref_sparse} Y.-C.\ Tsai, H.\ Hsiao, K.-Y.\ Chen, and S.-D.\
Lin, ``Concept-Aware Privacy Mechanisms for Defending Embedding
Inversion Attacks,'' \emph{arXiv:2602.07090}, 2026.

\bibitem{ref_nvdp} D.\ El Zein, S.\ Kumar, and J.\ Henderson,
``Nonparametric Variational Differential Privacy via Embedding Parameter
Clipping,'' \emph{arXiv:2603.09583}, 2026.

\bibitem{ref_mrl} A.\ Kusupati et al., ``Matryoshka Representation
Learning,'' in \emph{Advances in Neural Information Processing Systems},
2022.

\bibitem{ref_vec2vec} R.\ Jha, C.\ Zhang, V.\ Shmatikov, and J.\ X.\
Morris, ``Harnessing the Universal Geometry of Embeddings,''
\emph{arXiv:2505.12540}, 2025.

\bibitem{ref_zeng_rag} S.\ Zeng et al., ``The Good and the Bad:
Exploring Privacy Issues in Retrieval-Augmented Generation (RAG),''
in \emph{Findings of ACL}, 2024, pp.\ 4505--4524.

\bibitem{ref_song_leak} C.\ Song and A.\ Raghunathan, ``Information
Leakage in Embedding Models,'' in \emph{Proc.\ ACM CCS}, 2020,
pp.\ 377--390.

\bibitem{ref_shokri} R.\ Shokri et al., ``Membership Inference Attacks
Against Machine Learning Models,'' in \emph{Proc.\ IEEE S\&P},
2017, pp.\ 3--18.

\bibitem{ref_carlini} N.\ Carlini et al., ``Extracting Training Data
from Large Language Models,'' in \emph{Proc.\ USENIX Security},
2021, pp.\ 2633--2650.

\bibitem{ref_dwork} C.\ Dwork, ``Differential Privacy,'' in
\emph{Proc.\ ICALP}, 2006, pp.\ 1--12.

\bibitem{ref_analytic_gaussian} B.\ Balle and Y.-X.\ Wang,
``Improving the Gaussian Mechanism for Differential Privacy: Analytical
Calibration and Optimal Denoising,'' in \emph{Proc.\ ICML}, PMLR, vol.\ 80,
2018, pp.\ 394--403.

\bibitem{ref_dpsgd} M.\ Abadi et al., ``Deep Learning with Differential
Privacy,'' in \emph{Proc.\ ACM CCS}, 2016, pp.\ 308--318.

\bibitem{ref_lyu} L.\ Lyu, X.\ He, and Y.\ Li, ``Differentially Private
Representation for NLP,'' in \emph{Findings of EMNLP}, 2020,
pp.\ 2355--2365.

\bibitem{ref_kenthapadi} K.\ Kenthapadi, A.\ Korolova, I.\ Mironov, and
N.\ Mishra, ``Privacy via the Johnson-Lindenstrauss Transform,''
\emph{J.\ Privacy and Confidentiality}, vol.\ 5, no.\ 1, 2013.

\bibitem{ref_liu} K.\ Liu, H.\ Kargupta, and J.\ Ryan,
``Random Projection-Based Multiplicative Data Perturbation for Privacy
Preserving Distributed Data Mining,'' \emph{IEEE TKDE}, vol.\ 18,
no.\ 1, 2006, pp.\ 92--106.

\bibitem{ref_ckks} J.\ H.\ Cheon, A.\ Kim, M.\ Kim, and Y.\ Song,
``Homomorphic Encryption for Arithmetic of Approximate Numbers,'' in
\emph{Advances in Cryptology---ASIACRYPT 2017}, LNCS 10624, pp.\ 409--437.

\bibitem{ref_tenseal} A.\ Benaissa, B.\ Retiat, B.\ Cebere, and A.\ E.\
Belfedhal, ``TenSEAL: A Library for Encrypted Tensor Operations Using
Homomorphic Encryption,'' \emph{arXiv:2104.03152}, 2021.

\bibitem{ref_ckks_bootstrap} J.\ H.\ Cheon, K.\ Han, A.\ Kim et al.,
``Bootstrapping for Approximate Homomorphic Encryption,'' in
\emph{Advances in Cryptology---EUROCRYPT 2018}, LNCS 10820,
pp.\ 360--384.

\bibitem{ref_he_std} M.\ Albrecht et al., ``Homomorphic Encryption
Security Standard,'' HomomorphicEncryption.org, 2018.

\bibitem{ref_lwe_estimator} M.\ R.\ Albrecht, R.\ Player, and S.\ Scott,
``On the Concrete Hardness of Learning with Errors,'' \emph{Journal of
Mathematical Cryptology}, vol.\ 9, no.\ 3, 2015, pp.\ 169--203
(lattice-estimator methodology).

\bibitem{ref_schonemann} P.\ H.\ Sch\"onemann, ``A Generalized Solution
of the Orthogonal Procrustes Problem,'' \emph{Psychometrika}, vol.\ 31,
no.\ 1, 1966, pp.\ 1--10.

\bibitem{ref_cancellable} V.\ M.\ Patel, N.\ K.\ Ratha, and R.\ Chellappa,
``Cancelable Biometrics: A Review,'' \emph{IEEE Signal Processing
Magazine}, vol.\ 32, no.\ 5, 2015, pp.\ 54--65.

\bibitem{ref_openfhe} A.\ Al Badawi et al., ``OpenFHE: Open-Source Fully
Homomorphic Encryption Library,'' in \emph{Proc.\ WAHC '22},
2022, pp.\ 53--63.

\bibitem{ref_eva} R.\ Dathathri et al., ``EVA: An Encrypted Vector
Arithmetic Language and Compiler for Efficient Homomorphic
Computation,'' in \emph{Proc.\ ACM PLDI}, 2020, pp.\ 546--561.

\bibitem{ref_chet} R.\ Dathathri et al., ``CHET: An Optimizing Compiler
for Fully-Homomorphic Neural-Network Inferencing,'' in
\emph{Proc.\ ACM PLDI}, 2019, pp.\ 142--156.

\bibitem{ref_jung_gpu} W.\ Jung, S.\ Kim, J.\ H.\ Ahn et al.,
``Over 100x Faster Bootstrapping in Fully Homomorphic Encryption
through Memory-centric Optimisation with GPUs,'' \emph{IACR TCHES},
vol.\ 2021, no.\ 4, pp.\ 114--148.

\bibitem{ref_hexl} F.\ Boemer et al., ``Intel HEXL: Accelerating
Homomorphic Encryption with Intel AVX512-IFMA52,'' in
\emph{Proc.\ WAHC '21}, 2021, pp.\ 57--62.

\bibitem{ref_tiptoe} A.\ Henzinger, E.\ Dauterman, H.\ Corrigan-Gibbs,
and N.\ Zeldovich, ``Private Web Search with Tiptoe,'' in
\emph{Proc.\ ACM SOSP}, 2023.

\bibitem{ref_sealpir} S.\ Angel, H.\ Chen, K.\ Laine, and S.\ Setty,
``PIR with Compressed Queries and Amortised Query Processing,'' in
\emph{Proc.\ IEEE S\&P}, 2018, pp.\ 962--979.

\bibitem{ref_simplepir} A.\ Henzinger, M.\ M.\ Hong, H.\ Corrigan-Gibbs,
S.\ Meiklejohn, and V.\ Vaikuntanathan, ``One Server for the Price of
Two: Simple and Fast Single-Server Private Information Retrieval
(SimplePIR),'' in \emph{Proc.\ USENIX Security}, 2023.

\bibitem{ref_onionpir} M.\ H.\ Mughees, H.\ Chen, and L.\ Ren,
``OnionPIR: Response Efficient Single-Server PIR,'' in
\emph{Proc.\ ACM CCS}, 2021, pp.\ 2292--2306.

\bibitem{ref_halko} N.\ Halko, P.-G.\ Martinsson, and J.\ A.\ Tropp,
``Finding Structure with Randomness: Probabilistic Algorithms for
Constructing Approximate Matrix Decompositions,'' \emph{SIAM Review},
vol.\ 53, no.\ 2, 2011, pp.\ 217--288.

\bibitem{ref_pq} H.\ Jegou, M.\ Douze, and C.\ Schmid, ``Product
Quantisation for Nearest Neighbor Search,'' \emph{IEEE TPAMI},
vol.\ 33, no.\ 1, 2011, pp.\ 117--128.

\bibitem{ref_eckart} C.\ Eckart and G.\ Young, ``The Approximation of
One Matrix by Another of Lower Rank,'' \emph{Psychometrika}, vol.\ 1,
no.\ 3, 1936, pp.\ 211--218.

\bibitem{ref_jl} W.\ B.\ Johnson and J.\ Lindenstrauss, ``Extensions
of Lipschitz Mappings into a Hilbert Space,'' \emph{Contemporary
Mathematics}, vol.\ 26, 1984, pp.\ 189--206.

\bibitem{ref_bleu} K.\ Papineni et al., ``BLEU: a Method for Automatic
Evaluation of Machine Translation,'' in \emph{Proc.\ ACL}, 2002,
pp.\ 311--318.

\bibitem{ref_rag} P.\ Lewis et al., ``Retrieval-Augmented Generation
for Knowledge-Intensive NLP Tasks,'' in \emph{Proc.\ NeurIPS}, 2020.

\bibitem{ref_beir} N.\ Thakur, N.\ Reimers, A.\ R\"uckl\'e, A.\ Srivastava,
and I.\ Gurevych, ``BEIR: A Heterogeneous Benchmark for Zero-shot
Evaluation of Information Retrieval Models,'' in \emph{Proc.\ NeurIPS
Datasets and Benchmarks}, 2021.

\bibitem{ref_sse} R.\ Curtmola, J.\ Garay, S.\ Kamara, and R.\ Ostrovsky,
``Searchable Symmetric Encryption: Improved Definitions and Efficient
Constructions,'' in \emph{Proc.\ ACM CCS}, 2006, pp.\ 79--88.

\bibitem{ref_structenc} M.\ Chase and S.\ Kamara, ``Structured Encryption
and Controlled Disclosure,'' in \emph{Advances in Cryptology---ASIACRYPT},
2010, pp.\ 577--594.

\bibitem{ref_leakageabuse} D.\ Cash, P.\ Grubbs, J.\ Perry, and T.\
Ristenpart, ``Leakage-Abuse Attacks Against Searchable Encryption,'' in
\emph{Proc.\ ACM CCS}, 2015, pp.\ 668--679.

\bibitem{ref_accesspattern} M.\ S.\ Islam, M.\ Kuzu, and M.\ Kantarcioglu,
``Access Pattern Disclosure on Searchable Encryption: Ramification, Attack
and Mitigation,'' in \emph{Proc.\ NDSS}, 2012.

\bibitem{ref_v2t_repro} D.\ Seputis, Y.\ Li, K.\ Langerak, and S.\
Mihailov, ``Rethinking the Privacy of Text Embeddings: A Reproducibility
Study of `Text Embeddings Reveal (Almost) As Much As Text','' in
\emph{Proc.\ ACM RecSys}, 2025. \emph{arXiv:2507.07700}.

\bibitem{ref_vkit} S.\ M.\ Kurilenko, ``Hybrid Method for
Privacy-Preserving Semantic Search Based on Homomorphic Encryption and
Random Projections,'' \emph{Vestnik Komp'yuternykh i Informatsionnykh
Tekhnologiy}, no.\ 3, 2026, pp.\ 44--49.

\bibitem{ref_alpha} S.\ M.\ Kurilenko, ``Hybrid privacy-aware semantic
search: SVD-truncated document geometry and CKKS-encrypted query reranking
under a restricted threat model,'' \emph{arXiv:2606.26373}, 2026.

\bibitem{ref_steer} Z.\ Wan et al., ``Transform Before You Query: A
Privacy-Preserving Approach for Vector Retrieval with Embedding Space
Alignment (STEER),'' \emph{arXiv:2507.18518}, 2025.

\bibitem{ref_entroguard} S.\ Wang et al., ``Safeguarding LLM Embeddings in
End-Cloud Collaboration via Entropy-Driven Perturbation (EntroGuard),''
\emph{arXiv:2503.12896}, 2025.

\end{thebibliography}
